---
title: 'Lab 3: Data Wrangling on Soccer Tournament Data'
date: 'July 9, 2020'
output:
  pdf_document: default
  html_document: default
---
```{r setup, message = F, include=FALSE}
library(tidyverse)
```

Soccer tournament data wrangling
--------------------------
Read the dataset of football games.
```{r}
d <- read_csv("data/results.csv")
```

1. Select variables `date`, `home_team` and `away_team`.
```{r}
d %>% select(date, home_team, away_team)
```
2. Subset games with **Brazil** as the home team.
```{r}
d %>% filter(home_team == "Brazil")
```

3. Choose the games that Brazil won as the home team, and select variables `date`, `away_team` and `tournament`.
```{r}
d %>% filter(home_team=="Brazil", 
         home_score - away_score > 0) %>% 
  select(date, away_team, tournament)
```

4. Add the difference of goals, and an indicator variable called `goleada` for when the difference of goals is large,  and select what we did only for Brazil. **Hint: use `ifelse`**.
```{r}
d %>% 
  
  mutate(dif = abs(away_score - home_score),
            
         goleada = ifelse(dif > 5, "Goleada", "Normal  Result")) %>%
  
    filter(home_team=="Brazil" | away_team=="Brazil",
                 goleada=="Goleada")
```

5. What was the largest difference in goals within these games?
```{r}
d %>% 
  
  mutate(dif = abs(away_score - home_score)) %>%
  
  arrange(desc(dif)) %>%
  
  slice(1)  
```

6. The top 5 goleadas?
```{r}
d %>% 
  
  mutate(dif = abs(away_score - home_score)) %>%
  
  arrange(desc(dif)) %>%
  
  slice(1:5) # top_n(5) here would also do the trick
```
7. Summary on goals scored by home teams, such as `mean` of `home_score` and `away_score`, `std`, using `group_by` and `summarise`
```{r}
d %>% 
  
  group_by(home_team) %>%
  
  summarise(mean_home_gols= mean(home_score, na.rm = TRUE), 
            sd_home_gols= sd(home_score), 
            mean_home_gols_op = mean(away_score), 
            count=n()) %>%
  
  ungroup() %>%
  
  top_n(., 10, wt=mean_home_gols)  # note here, it does 
                                  # not give you in order
                                  # you can add arrange
```

8. Proportion of victories of **Brazil** on different tournaments against each opponent, for instance, **Argentina**.
```{r}
d %>% 

  filter(home_team=="Brazil") %>%
  
  mutate(dif = home_score - away_score, 
         victory = ifelse(dif>0, 1, 0)) %>%
  
  group_by(away_team, tournament) %>%
  
  summarise(mean_victory_brazil= mean(victory, na.rm = TRUE), 
            number_games=n()) %>%
  
  filter(away_team=="Argentina")
```
